\LARGE BAND\\ \Large Unleashing Tokenized Economy

### 2018-02-26 paper.tex
Finish first pass introduction

\subsection{Use Cases}

>>>>

\subsection{Token-curated Community}
Typically, economy centers around community with common shared interest. There are multiple layers of community depending on the focus. A country is one big community where everyone shares geographical border, culture, tradition, customs and beliefs. Soccer players and followers together is another community where everyone shares interest in the sport which leads to an economic activity around soccer team and players. This leads to two sides of participant in the community: buyers and sellers. While they share similar interest in the same community, they often have conflicting needs as both sides try to maximize their own utility at the expense of the other side. Soccer team would raise their ticket price as they gain more popularity while their loyal followers have to keep paying more. Conversely, followers will not go out of their way to promote their favorite artist because they have very little economic incentive to do so. Their incentives are not truly aligned.

Crypto asset becomes the answer to which community members can finally have an aligned incentive to grow the community together. A token-curated community is a community centered around a personalized Community Token whose value closely tie to the overall network value of the community. Community Token acts as a shared economic incentive for both buyers and sellers to promote the growth of the community. Band Protocol standardizes the creation of token-curated community and details how personalized Community Token's value can be derived from overall community value through staking and discount mechanism.

%Currently companies, brands and celebrities struggle to engage with their loyal customers and followers. They mostly utilize social media channels such as Facebook, Twitter, and Instagram to cultivate their community. However, it is becoming more difficult to monetize their fan base. Many celebrities try to monetize their followers by advertising products from other companies to their followers, which is not always in the best interest of the community. For example, recent Thai celebrities are facing lawsuit because they advertise non-FDA-approved cosmetics. Influencers accept payment to promote products inorganically which misleads their followers. Similarly, content distributor channel like Youtube and Spotify are taking a big cut from content provider. Newcomers find themselves much more difficult to compete for attention and create network effect, which was originally promised by these platforms.

\subsection{Use Cases}
\begin{itemize}
\item A new musician creates a new community and publishes her first album. She cultivates and rewards early adopters through her Community Token. By having skin-in-the-game token, early adopters rally behind her success and help her grow the community.
\item Bruno Mars issue Bruno Token which can be staked to receive constant discount for all future products, priority queue to purchase concert ticket, and right to access VIP zone during meet and greet session. Bruno Mars also sell rare digital cards which contain non-public photos of the band and digital artwork.
\item Established company creates a community to curate information around a company and reward active participants with community token. Similar to how Barilla encourages followers to post new recipe on Facebook Page, now active participants can receive Barilla Token to purchase Barilla products as an incentive to curate information inside Barilla community.
\end{itemize}

\subsection{BAND Architecture} \label{sec:band-architecture}

BAND architecture consists of three main layers shown in figure~\ref{fig:pyramid}:

\begin{itemize}
\item \textbf{BAND Blockchain Layer} provides backbone blockchain network to support the entire BAND ecosystem. This includes design of cryptographic algorithm for public-private key management, gas allocation, blockchain internal state representation, on-chain price oracle and native BAND Token.
\item \textbf{BAND Protocol Layer} provides standard contracts to facilitate tokenized economy by enabling creation of personalized-token-curated community, tokenized products, token subscription model, discount token, attention curation market, etc.
\item \textbf{Application Layer} is the consumer-facing application that utilize the underlying BAND blockchain and protocol and serve real-world needs. Any developers can create a solution on top of open, permissionless BAND Protocol. Campbase will be the first application built on top of BAND.
\end{itemize}

\begin{figure}[h]
    \centering
    \includegraphics[width=1.05\textwidth]{figures/pyramid}
    \caption{Overview of BAND architecture}
    \label{fig:pyramid}
\end{figure}

\clearpage
\newpage
